(Automatic) Speech Recognition Project --- Attacks on Neural Networks in a Lightweight Speech Anonymization Pipeline

### 2024-05-27 paper/paper.tex
Finished related works section (for now)

\subsection{Attacks on Neural Networks}
The FGSM attack used by \citet{shihao2024adversarial} is an example of an adversarial attack.
Adversarial attacks are extensively described by \citet{xiaoyong2019adversarial}.
They provide an introduction to and an overview of adversarial attacks within the deep learning domain, and should provide the reader with plentiful knowledge on the topic.

@@

\subsection{Attacks on Neural Speech Systems}
\citet{chen2022survey} % Survery about adversarial attacks on ASR models

\citet{neekhara2019universal} % Paper about adversarial attacks on ASR systems

\citet{kreuk2018fooling} % Paper about adversarial attacks on E2E speaker verification

>>>>

\subsection{Adversarial Attacks on Neural Networks}
The FGSM attack used by \citet{shihao2024adversarial} is an example of an adversarial attack.
Adversarial attacks are extensively described by \citet{xiaoyong2019adversarial}.
They provide an introduction to and an overview of adversarial attacks within the deep learning domain, and should provide the reader with plentiful knowledge on the topic.
\citet{chen2022survey} provide an overview of adversarial attacks aimed at speech systems, including ASR systems.

@@

%%%%% Low priority, not needed for understanding the project, so only write if there's time left.
% \subsection{Adversarial Attacks on Neural Speech Systems}
% As demonstrated by \citet{liu2018trojaning,stefanos2022ultrasonic,stefanos2023jingleback}, neural ASR systems are shown to be susceptible to backdoor attacks.
% The range of adversarial attacks aimed at neural speech systems is not limited backdoor attacks, however.

% \citet{carlini2018audio}
% \citet{alzantot2018didyouhearthat}
% \citet{carlini2016hiddenvc}
% \citet{iter2017generating}
% \citet{vaidya2015cocainenoodles}
% \citet{neekhara2019universal}
% \citet{kreuk2018fooling}
